---
title: "Day 03 HW"
output: html_notebook
---

```{r}
library(broom)
library(GGally)
library(tidyverse)
library(janitor)
library(factoextra)
mall_customers <- read.csv("data/mall_customers.csv")%>% 
  clean_names()
```


```{r}
# mall_customers %>% 
#   group_by(gender) %>% 
#   summarise(gender_count = sum(gender) / n())
```


1.
```{r}
# mall_customers %>% 
#   mutate(spending_rate = spending_score_1_100 / n())

mall_customers %>% 
  group_by(gender) %>% 
  ggplot(aes(y = annual_income_k, x = spending_score_1_100, colour = gender)) +
  geom_point()

mall_customers %>% 
  ggplot(aes(x = gender, y = spending_score_1_100)) +
  geom_bar(stat = "identity")


```

Women spend more than men, spending score doesn't seem correlated with annual_income_k which is surprising. Age also seems unrelated to annual income unexpectedly.

2.
```{r}
# first we scale the data
mall_customers_scale <- mall_customers %>% 
  mutate(across(c(annual_income_k, spending_score_1_100), scale))

# then let's find a good value for k
fviz_nbclust(mall_customers_scale %>% select(annual_income_k, spending_score_1_100),
             FUNcluster = kmeans,
             method = "wss",
             nstart = 20)

fviz_nbclust(mall_customers_scale %>% select(annual_income_k, spending_score_1_100),
             FUNcluster = kmeans,
             method = "silhouette",
             nstart = 20)

fviz_nbclust(mall_customers_scale %>% select(annual_income_k, spending_score_1_100),
             FUNcluster = kmeans,
             method = "gap_stat",
             nstart = 20)

# we will choose 4 as either 4 or 5 or 1 are suggested by these plots

```


```{r}
# now we set up kmeans and plug it into augment() to visualise our clusters
set.seed(123)

kmeans_mall <- kmeans(
  mall_customers_scale %>% select(annual_income_k, spending_score_1_100), 
  centers = 4, 
  nstart = 20)

augment(kmeans_mall, mall_customers) %>% 
  ggplot(aes(spending_score_1_100, annual_income_k, colour = .cluster)) +
  geom_point()
```

The clustering looks ok to me.

The light blue cluster (#3) is high spenders with low income.
the red group is low spenders and low income
the green group is high income and low spend
the purple group is high income and high spend

