---
title: "Hypothesis Testing"
output: html_notebook
---

1.1 Hypothesis testing - practical

1.
```{r}
library(tidyverse)
library(infer)
data(msleep)
```


2.
Is the mean(sleep_total) the same as the jaberwockies sleep total (7 hours)?

alpha; 0.05
HO; mean(sleep_total) - 7 = 0
HA; mean(sleep_total) - 7 != 0

Calculate test statistic
```{r}
mean_diff_sleep <- mean(msleep$sleep_total) - 7
```

Mean is much higher than 7. HA is likely true

```{r}
null_distribution <- msleep %>% 
  specify(response = sleep_total) %>%    # response = what we care about (average rating)
  hypothesise(null = "point", mu = mean_diff_sleep) %>%  # this time we also hypothesise
  generate(reps = 2000, type = "bootstrap") %>%   # type will change for different tests
  calculate(stat = "mean")
```

```{r}
null_distribution_q3 %>% 
  visualise(bins = 25) +
  shade_p_value(obs_stat = mean_diff_sleep,
                direction = "both")
```

It doesn't even show up! It's totally off

```{r}
null_distribution %>% 
  get_p_value(
    obs_stat = mean(msleep$sleep_total),
    direction = "both")
```

p is <0.001! Meaning we can reject the null hypothesis


3.
Perform an appropriate statistical test to determine whether omnivores sleep for significantly longer than herbivores, on average.

Average means we're working with mean.

Basically, group by diet type then mean(sleep_total)


Start with herbivores
```{r}
avg_herbi <- msleep %>% 
  filter(vore == "herbi") %>% 
  group_by(vore) %>% 
  summarise(mean = mean(sleep_total))

avg_omni <- msleep %>% 
  filter(vore == "omni") %>% 
  group_by(vore) %>% 
  summarise(mean = mean(sleep_total))
```

avg_herbi = 9.5

HO: avg_omni - 9.5 = 0
HA: avg_omni - 9.5 > 0



```{r}
mean_diff <- avg_omni$mean - avg_herbi$mean

null_distribution_q3 <- msleep %>% 
  specify(response = sleep_total) %>%    # response = what we care about (average rating)
  hypothesise(null = "point", mu = mean_diff) %>%  # this time we also hypothesise
  generate(reps = 10000, type = "bootstrap") %>%   # type will change for different tests
  calculate(stat = "mean")
```

```{r}
null_distribution_q3 %>% 
  visualise(bins = 25) +
  shade_p_value(obs_stat = mean_diff,
                direction = "greater") # direction depends on your hypothosese 

null_distribution_q3 %>% 
  get_p_value(
    obs_stat = mean_diff,
    direction = "less")
```

p > alpha, therefore we can NOT reject the null hypothesis.


4. Perform an appropriate statistical test to determine whether the proportion of domesticated animal types in the population of animal types is greater than 5%

one sample prop, therefore:
```{r}
# one sample prop
data %>% 
  specify(response = "col of interest", success = "success condition") %>% 
  hypothesise(null = "point", p = x) %>% 
  generate(reps = yyyy, type = "draw") %>% 
  calculate(stat = "prop")
```


H0: prop_domesticated animals = 0.05
HA: prop_domesticated animals > 0.05
```{r}
msleep <- msleep %>% 
  mutate(is_domesticated = conservation == "domesticated")
```


Calculate test statistic
```{r}
prop_domesticated <- msleep %>% 
  filter(is_domesticated == TRUE) %>% 
  summarise(prop = n() / nrow(msleep))
```


```{r}
null_distribution_q4 <- msleep %>% 
  drop_na() %>% 
  specify(response = is_domesticated, success = 'TRUE') %>% 
  hypothesise(null = "point", p = 0.05) %>% 
  generate(reps = 2000, type = "draw") %>% 
  calculate(stat = 'prop')
```
```{r}
null_distribution_q4 %>% 
  visualise(bins = 25) +
  shade_p_value(obs_stat = prop_domesticated,
                direction = "greater") # direction depends on your hypothosese 

null_distribution_q4 %>% 
  get_p_value(
    obs_stat = prop_domesticated,
    direction = "greater")
```

p > 0.05, therefore we may not reject the null hypothesis in favour of HA.




1.2 Hypothesis testing - Defining the Hypothesis

For the following three business problems write out:

What kind of test you would use
H0
 and Ha
 in both mathematical notation and in words.
Also state the method you would use to generate the null distribution (bootstrap, permutation or draw).


1.
Boss thinks that 40% of the town knows about the coffee shop. I think it is higher than 40%

I have one sample of 200 and I am working with proportions, I would perform a draw (one sample proportion) test.

H0: people_knowing_about_coffee_shop = 0.4
HA; people_knowing_about_coffee_shop > 0.4


2.
"that website users overall are more likely to click on the banner if positioned at the top of the page"

Group A
 continued to be shown the banner at the right hand side of the webpage (its usual position)
 
  group B
 was shown the banner at the top of the page
 
 proportion
 
Will the CTR (click through rate) be higher for group B?

H0: CTR_group_A - CTR_group_B >= 0
HA: CTR_group_A - CTR_group_B < 0

H0: Those in group A (banner at right of page), are more likely to click (have a higher CTR) than those of group B (banner at TOP of page)

HA: Those in group A(banner at right of page), are less likely to click (have a higher CTR) than those of group B (banner at TOP of page)

I would use two-sample independent testing, with permutations.



3.
H0: mean_part_width - 145 = 0
HA: mean_part_width - 145 != 0

H0: the mean_part_width is 145mm
HA: the mean_part_width is not 145mm

We have one sample only. We are dealing with means rather than proportions. Therefore we will use bootstrapping


1.3 Hypothesis Testing - Interpreting the results
1.
H0: people_knowing_about_coffee_shop = 0.4
HA; people_knowing_about_coffee_shop > 0.4

Coffee shop problem. Significance level: 0.05, calculated p
-value: 0.07

If p > alpha, we can't reject the null hypothesis.
0.07 > 0.05

We can't reject the null hypothesis.


2.
H0: CTR_group_A - CTR_group_B >= 0
HA: CTR_group_A - CTR_group_B < 0

Website company problem. Significance level: 0.01, p
-value: 0.006

If p > alpha, we can't reject the null hypothesis.
0.01 > 0.006 = FALSE
We CAN reject the null hypothesis




3.
H0: mean_part_width - 145 = 0
HA: mean_part_width - 145 != 0

Manufacturing company problem. Significance level: 0.05, p
-value: 0.55

If p > alpha, we can't reject the null hypothesis.

0.055 > 0.05
We may not reject the null hypothesis.
