---
title: "Distributions Homework"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(skimr)
phones <- read_csv("data/20190928-items.csv") %>% 
  clean_names()
```

1. Exploration
```{r}
view(phones)
skim(phones)

ggplot(phones) +
  aes(x = )
```


```{r}
phones %>% 
  group_by(brand) %>% 
  summarise(x = n()) %>% 
  arrange(desc(x)) %>% 
  head(1)

# Samsung has the most phones
```


```{r}
rating_phones <- phones %>% 
  filter(brand == "Samsung") %>%
  summarise(
    num = n(),
    mean = mean(rating),
    sd = sd(rating)
  )
  
phones %>% 
  filter(brand == "Samsung") %>% 
  ggplot(aes(x = rating)) +
  geom_histogram(aes(y = ..density..),
                     col = "white",
                     bins = 25) +
  stat_function(
    fun = dnorm,
    args = list(
      mean = rating_phones$mean,
      sd = rating_phones$sd
    ),
    col = "red"
  )
```

```{r}
phones %>%
  filter(rating >= rating_phones$mean - rating_phones$sd) %>%
  filter(rating <= rating_phones$mean + rating_phones$sd) %>%
  summarise(prop_within_1sd = n() / nrow(phones))

phones %>%
  filter(rating >= rating_phones$mean - (rating_phones$sd * 2)) %>%
  filter(rating <= rating_phones$mean + (rating_phones$sd * 2)) %>%
  summarise(prop_within_2sd = n() / nrow(phones))

phones %>%
  filter(rating >= rating_phones$mean - (rating_phones$sd * 3)) %>%
  filter(rating <= rating_phones$mean + (rating_phones$sd * 3)) %>%
  summarise(prop_within_3sd = n() / nrow(phones))
```

Fairly close to what you'd expect from a normal distribtion, particulary as you get further away from the mean.


```{r}
qqnorm(trees$Height)
```

2 Extension
Investigate the use of the qqnorm() plot in R to determine whether data is normally distributed. What is a ‘quantile-quantile plot’? What do we expect to see in a qqnorm() plot if data is nearly normally distributed?

```{r}
qqnorm(y = phones$rating, pch = 1, frame = FALSE) +
qqline(y = phones$rating, col = "blue", lwd = 2)
```

I'm not quite sure, it looks normal.
