---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
books <- read_csv("data/books.csv")
```

```{r}
view(books)

glimpse(books)
```
possible areas to explore:

1. The publisher, what  if we grouped by Publisher and some other categories, we could do some comparisons.

2. What about authors, how about we find how many books each author has published? See who has the most and the least

3. What about languages, see which languages are the most common.

4. Who is the most popular author? (by average_rating)



1. Which publisher has published the most books?

Note: I was trying to answer question 3 and struggling - I inadvertently answered this one instead!

```{r}
books1  <-  books %>% 
  select(publisher) %>% 
  group_by(publisher) %>% 
  summarise(count_of_books_published = n()) %>% 
  arrange(desc(count_of_books_published))

head(books1)

# Answer - vintage!

```


2. What are the top 5 rated books?
```{r}
books2 <- books %>% 
  arrange(desc(average_rating)) %>% 
  select(average_rating, title)

head(books2, 5)

view(books2)

```

This does seem to be right; however, there are actually 22 books tied for first place! These 5 are randomly selected, not inherently higher rated than any of the other 22. We could use distinct to filter out equal ratings - but then it's even less accurate!




3. Which publisher has the best rating?



```{r}
books3  <-  books %>% 
  select(publisher, average_rating) %>% 
  group_by(publisher) %>% 
  summarise(mean_of_ratings = mean(average_rating)) %>% 
  arrange(desc(mean_of_ratings))

head(books3, 12)

# These are the 12 publishers with the highest average ratings.

```

4. 

How many book are published in English?

```{r}
books4 <- books %>% 
  group_by(language_code) %>% 
  summarise(book_count_per_language = n()) %>% 
  arrange(desc(book_count_per_language))

books4

8909 + 1408 + 214 + 7


```

There are 10538 books published in English.


5.

What is the percentage of English books published to other languages?

```{r}
books5 <- books %>% 
  group_by(language_code) %>% 
  summarise(book_count_per_language = n()) %>% 
  arrange(desc(book_count_per_language)) %>% 
  filter(language_code != "eng", 
         language_code != "en-US",
         language_code != "en-CA", 
         language_code != "en-GB") %>% 
  summarise(not_english_books = sum(book_count_per_language))

books6 <- books %>% 
  group_by(language_code) %>% 
  summarise(book_count_per_language = n()) %>% 
  arrange(desc(book_count_per_language)) %>% 
  filter(language_code == "eng" | 
         language_code == "en-US" |
         language_code == "en-CA" |
         language_code == "en-GB") %>% 
  summarise(english_books = sum(book_count_per_language))

percentage_of_non_english_to_english_books <- books5 / books6 * 100

round(percentage_of_non_english_to_english_books, 2)


```

Non-English books represent 5.56% of the books in our dataset.

