---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
movies <- read_csv("movies.csv")
```

1.
```{r}
view(movies)

glimpse(movies)
```

To start with, I'd use view() and glimpse() functions to get an overview of the data.

I'd check to see if there are any differences between original_movie and movie, as most of them seem the same.

Homepages seem to have a lot of NAs, I can't  see  this being a big issue though; it doesn't seem like important information anyway (could be wrong though!)

I might want to sort by release date and use arrange() on it, it's out of order.

I'd check for NA values in different variables.

2. 
```{r}
movies_selected <- movies %>%
  select(runtime, title, budget)
  

```

3. 

```{r}


runtime_count <- movies_selected %>% #Assign a variable runtime_count
  filter(is.na(runtime)) %>%  #Filters out the na variables and returns them
  summarise(count = sum(is.na(runtime))) # creates a new data frame of the sum of all na values

budget_count <- movies_selected %>% # same but for budget column
  filter(is.na(budget)) %>% 
  summarise(count = sum(is.na(budget)))

title_count <- movies_selected %>% #same butfor title count  column
  filter(is.na(title)) %>%
  summarise(count = sum(is.na(title)))

runtime_count + budget_count + title_count #Add all 3 counts together, to get the total number of na values

summary(movies_selected) # this will tell us NAs, little hack



movies_selected %>% 
  summarise(across(everything(), ~sum(is.na(.x))))
  
```

4. 
```{r}
movies_na_count_updated <- movies_selected %>%  # Assigning a new variable, for the updated count which we'll return at the end
  mutate(runtime = na_if(runtime, 0)) %>%  # Mutates the column runtime, so that it will register as NA if a 0 is found in any of the rows
  summarise(count = sum(is.na(runtime))) # Creates a new dataframe of the sum of all NA values, this time including Os as NAs
  

movies_na_count_updated
```


5. 
```{r}


movies_imputed <- movies_selected %>%
  mutate(runtime = na_if(runtime, 0)) %>% 
  mutate(runtime = coalesce(runtime, median(runtime, na.rm = T)))


movies_imputed %>% 
  summarise(count = sum(is.na(runtime)))


```
6.

```{r}
movies_imputed %>% 
  arrange(desc(runtime)) %>% 
  head(10)
  
movies_imputed %>% 
  arrange(runtime) %>% 
  head(10)


longest_10 <- movies_imputed %>% 
  slice_max(runtime, n = 10)

shortest_10 <- movies_imputed %>% 
  slice_min(runtime, n = 10)

shortest_10

sum(1, 6, 2 ,3 ,4 ,5 ,7, NA, na.rm =  T)

```

7. 

```{r}
movies_imputed <- movies_imputed %>% 
  mutate(budget = if_else(budget < 100, median(budget), budget))


median(movies_imputed$budget)

movies_imputed %>% 
  filter(budget == median(budget))
```

Extension:

1.

```{r}
movie_budgets <- movies_imputed %>% 
  mutate(budget_type = case_when(
    budget < 12e6 ~ "Small budget",
    budget > 12e6 & budget < 40e6 ~ "Medium budget",
    budget >= 40e6 ~ "Big budget"
  ))


```

2. 
```{r}

character_columns <- movies %>% 
  select(where(class(character)))




movies %>% 
  summarise(
    across(.cols = where(is.character(),
           .fns = NULL,
           na.rm = T)))
  )

# This is Sarah's code
movies %>% 
    select(where(is.character)) %>% 
    summarise(
    across(.cols = where(is.character),
                .fns = ~sum(is.na(.x)))
                )

```



