---
title: "Day 1 HW"
output: html_notebook
---

Loading data in:
```{r}
library(tidyverse)
library(modelr)
library(broom)
project <- read_csv("data/project_management.csv")
```


Plotting data:
```{r}
model <- lm(actual_length ~ estimated_length,
            data = project)

project %>% 
  ggplot() +
  aes(x = estimated_length, y = actual_length) +
  geom_point()
  #geom_smooth(method = "lm")
```


Calculating correlation coefficient:
```{r}
project %>% 
  summarise(correlation_coefficient = cor(y = actual_length, x = estimated_length))
```

A correlation coefficient of 0.8 indicates a very strong correlation


Performing a simple linear regression:
```{r}
model <- lm(actual_length ~ estimated_length,
            data = project)
```


Interpret the regression coefficient of estimated_length:
```{r}
glance(model)
```

0.65 means 65% of the actual_length can be explained by the estimated_length.


Is the relationship statistically significant?
```{r}
tidy(project)
```
Yes cause of the small p-value


EXTENSION:
```{r}
aes(label = 1:nrow(project))

project %>% 
  ggplot() +
  aes(x = estimated_length, y = actual_length) +
  geom_text(aes(label = 1:nrow(project)))
```
5 looks like an outlier

