---
title: "Titanic Homework"
output: html_notebook
---

```{r}
library(tidyverse)
library(gtools)
source("prob.R")
titanic <- read_csv("data/titanic.csv")
```

Titanic:

```{r}
titanic %>% 
  select(class) %>% 
  unique()

titanic <- titanic %>% 
  mutate(passenger = class == "3rd" | class == "2nd" | class == "1st") %>% 
  mutate(crew = class != "3rd" & class != "2nd" & class != "1st")
```

What proportion of the crew survived? And what proportion of the passengers?

```{r}
total_survivors <- titanic %>% 
  filter(survived == "yes") %>% 
  nrow()

crew_survived_sum <- titanic %>% 
  filter(crew == TRUE & survived == "yes") %>% 
  nrow()

passenger_survived_sum <- titanic %>% 
  filter(crew == FALSE & survived == "yes") %>% 
  nrow()

prop_survived_crew <- crew_survived_sum / total_survivors

prop_survived_passenger <- passenger_survived_sum / total_survivors



prop_survived_crew
prop_survived_passenger

```

So; 
prob(survived | crew) = 0.3
prob(survived | passenger) = 0.7

Therefore, passengers were more likely to survive than crew.



Probability Consolidation Questions:

1.
```{r}
s_all_possibilities <- rolldie(1) %>% 
  summarise(all_possibilities = n())

s_less_5 <- rolldie(1) %>% 
  filter(X1 < 5) %>% 
  summarise(n())

prob_q1 <- s_less_5 / s_all_possibilities
prob_q1
```

2.
There are 3 events. 

```{r}
rolldie(3) %>% 
  summarise(n())

# and 216 possible outcomes
```

6.
P(A | B) = P(A AND B) / P(B)
P(spades | black) = P(spades) AND P(black) / P(black)

So, 26 of the cards are black. 13 are black and spades. So 13 is the intersect. According to the formula, this means 13/26 is the probability, or 0.5. 

This makes sense, as there is an equal chance of picking up a spade and a club.
```{r}
deck <- cards(jokers = FALSE) %>% 
  mutate(black_card = suit == "Club" | suit == "Spade")



```

4.
```{r}
heights <- c(100, 200, 300, 400, 500)

x <- as_tibble(permutations(n = 5, r = 5, v = heights))

1 / nrow(x)
```

5. 