---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```
1. 


Precipitation, temperature and wind speed are at 12pm.

Wind speed is in kph.
Temperature is in celsius.

```{r}


Thu <- list(temp = 10, chance_of_rain = 65, wind_speed = 20)
Fri <- list(temp= 11, chance_of_rain = 52, wind_speed = 16)
Sat <- list(temp = 8, chance_of_rain = 0, wind_speed = 11)

weather <- list(Thu = Thu, Fri = Fri, Sat = Sat)

weather


```

2.
```{r}
#i
weather$Thu$chance_of_rain

#ii
weather$Fri$wind_speed

#iii
weather$Thu$temp


```

3. 
```{r}
fourteen_day_forecast <- matrix(c(10, 11, 8, 8, 8, 7, 8, 9, 9, 9, 8, 8, 8, 8), nrow = 2, ncol = 7, byrow = TRUE)

fourteen_day_forecast
```

4.
```{r}
#i
fourteen_day_forecast[2,3]

#ii
fourteen_day_forecast[2,]

#iii
fourteen_day_forecast[c(1,2), c(1, 3, 5)]
```

5.
failed piece of code...
```{r}
answerer <- function(x){
  if (is.character(x) == TRUE){
    str_c("The answer is: ", x)
    
    if (is.numeric(x) == TRUE & x >= 10){
      return(x / 10)
    }  
        else {
            return(x)
    }
}} 
      
    print("Invalid input")
  


answerer("hel")
```

Got it to work!
```{r}
answerer2 <- function(x){
  if (is.character(x) == TRUE){
      str_c("The answer is: ", x)
  }
  else if (is.numeric(x) == TRUE & x > 10){
      return(x / 10)
  }
  else if (is.numeric(x) == TRUE & x < 10){
      return(x)
  } else {
      print("Invalid input")
  }
}

answerer2("hi")
answerer2(TRUE)
answerer2(9)
answerer2(11)


```

6. 
```{r}
vector_checker <- function(x, y){
  if (sort(x) == sort(y)){
    return("Exactly the same.")
  }
  else if (c(x) == c(y)){
    return("The same")
  }
}

test_vector <- c(1, 2, 3, 4)
test_vector2 <- c(4, 3, 2, 1)
test_vector3 <- c(5, 6, 7, 8)

vector_checker(test_vector, test_vector2)
```

```{r}
vector_checker <- function(x, y){
  if (all((x)) == all((y))){
    return("The same")
  }
  
  if (all(sort(x)) == sort(y)) {
    return("The same")
  }
}

test_vector <- c(1, 2, 3, 4)
test_vector2 <- c(4, 3, 2, 1)
test_vector3 <- c(5, 6, 7, 8)
test_vector4 <- c(1, 2, 3, 4)

vector_checker(test_vector, test_vector4)
```

1. if x and y are exactly the same
1.1   return exactly the same

2. if x and y are similar
2.1   return they are similar

3. return different
```{r}
x <- c(1, 2, 3)
y <-c(1, 2, 3)
z <- c(3, 2, 1)

#1. if x and y are exactly the same
if (identical(x, y)) {
  print("Exactly the same")
}

#2. if x and y are similar
if (identical(sort(x), sort(y))) {
  print("The same")
}

#3. return different
print("Different")
```

```{r}
is_similar <- function(x, y) {
  
  #1. if x and y are exactly the same
  if (identical(x, y)) {
    return("Exactly the same")
  }
  
  #2. if x and y are similar
  if (identical(sort(x), sort(y))) {
    return("The same")
  }
  
  #3. return different
  return("Different")
}

vector_1 <- c(1, 2, 3)
vector_2 <- c(3, 2, 1)
vector_3 <- c(4, 2, 1)

is_similar(x = vector_1, y = vector_1)
```

Note: return() kicks you out of the function

Questoin 7

1 2 3 
2 4 6
3 6 9


1. make an empty 12*12 matrix

2. loop through the matrix
2.1 set each cell value = row number * column number

```{r}
# 1. make an empty matrix
m <- matrix(nrow = 12, ncol = 12)


# 2. loop through the matrix
#2.1 for the number of rows
for(i in 1:nrow(m)) {
  print(i)
  print("Row i: ")
  # 2.2. for the number of columns
  for (j in 1:ncol(m)) {
    #2. 3 set each cell value = row number * column number
    m[i, j] <- i * j
  }
}

m
```

i = iterator



